Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-20 paper/ms.tex
add rotation plot

TESS photometric rotation period = 3.5days ish.

vsini = 17.48 $\pm$ 0.15 (CHIRON).

The two agree.

For comparison, gyrochrones would predict X.XX.

@@

>>>>

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Rotation periods for \tn\ and selected open clusters.}
    The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
    (1000$\,$Myr) are shown.  Their rotation periods were measured by
    \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
    and \citet{curtis_temporary_2019}, respectively.
    \label{fig:rotation}
	}
\end{figure}

TESS photometric rotation period = 3.5days ish.
vsini = 17.48 $\pm$ 0.15 (CHIRON).
The two agree.

For comparison, gyrochrones would ``predict'' X.XX.

@@

Figure~\ref{fig:rotation} compares the stellar rotation period of \tn\ to
periods that have been measured in a number of well-studied open clusters.
\tn\ seems to be gyrochronologically coeval with the Pleiades sequence.

We note that this is still in the ``sub 500 Myr'' range, when classical
Skumanich spin-down is not expected to be happening (why is this the number?).

This agrees with recent empirical results from Rebull et al 2020 and perhaps also 2018(?):
they observed the Taurus foreground (age 30 Myr) and saw that it was 
roughly consistent with the Pleaides.
Upper Sco had a consistent mean, but a much larger scatter.

%NOTE: begs the question... is there a large population of ~30-50 Myr old
% stars for which we could measure the rotation periods, and clarify if the scatter of Upper Sco chills out?
